\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Fix newly introduced typo

\section{Qualitative Testing}
\label{sec:qualitative}
We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time identify stumbling points in the interface.
At the completion of the task, we interviewed our participants to gather explanatory data and their opinions.

>>>>

\section{Qualitative Testing}
\label{sec:qualitative}
We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and identify stumbling points in the interface.
At the completion of the task, we interviewed our participants to gather explanatory data and their opinions.
